\textbf{Advection versus diffusion in intraventricular transport}

### 2025-03-25 paper/main.tex
add A-D eq. stability references

\subsection{Computational modeling aspects}
We modeled motile cilia as a stress
exerted tangentially on the CSF at the ventricular walls
while employing a slip boundary condition,
motivated by experimental observations of the
flow field in zebrafish embryo brain ventricles, both previously and in this work, in which
the fluid velocity increases towards the
wall~(\Crefpanels{fig:fig1}c)~\cite{Olstad2019CiliaryDevelopment}. 
The BDM-DG scheme ($\mathrm{BDM}_1$-$\mathrm{DG}_0$) we used to discretize the
governing equations of the flow is computationally more expensive
than more conventional approaches such as a
Taylor-Hood discretization
($P_2-P_1$ elements)~\cite{Stenberg1990ErrorProblem}, or lower-order enriched
elements, such as the mini-element
($P_1-P_1$ with a velocity stabilization)~\cite{Brezzi2011MixedMethods}.
Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
than or equal to $k$.
We opted for the BDM-DG scheme because of its exactly-mass-conserving property;
by the definition of the elements, the numerical approximation of
the CSF velocity satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}).
This leads to $\normlinf{\nabla\cdot\uu_h}$ being equal to zero to within solver tolerances,
an important property for the stability of the advection-diffusion equation\cite{CITATION}.
In addition to its favorable mass-conserving property, the 
Brezzi-Douglas-Marini and discontinuous Galerkin (BDM-DG) discretization scheme 
we employed for the Stokes equations
lets us impose the impermeability condition strongly, and the tangential
traction boundary condition weakly, without any tailored approach,
since these boundary conditions appear naturally in the weak form of the
Stokes equations~(\Cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
elements were to be used, the impermeability boundary condition must
be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
Bertoluzza2017BoundaryHemodynamics}.

>>>>

\subsection{Computational modeling aspects}
We modeled motile cilia as a stress
exerted tangentially on the CSF at the ventricular walls
while employing a slip boundary condition,
motivated by experimental observations of the
flow field in zebrafish embryo brain ventricles, both previously and in this work, in which
the fluid velocity increases towards the
wall~(\Crefpanels{fig:fig1}c)~\cite{Olstad2019CiliaryDevelopment}. 
The BDM-DG scheme ($\mathrm{BDM}_1$-$\mathrm{DG}_0$) we used to discretize the
governing equations of the flow is computationally more expensive
than more conventional approaches such as a
Taylor-Hood discretization
($P_2-P_1$ elements)~\cite{Stenberg1990ErrorProblem}, or lower-order enriched
elements, such as the mini-element
($P_1-P_1$ with a velocity stabilization)~\cite{Brezzi2011MixedMethods}.
Here, $P_k$ is the space of continuous Lagrange polynomials of degree less
than or equal to $k$.
We opted for the BDM-DG scheme because of its exactly-mass-conserving property;
by the definition of the elements, the numerical approximation of
the CSF velocity satisfies the continuity equation (\Cref{eq:stokes_eqs_cont}).
This leads to $\normlinf{\nabla\cdot\uu_h}$ being equal to zero to within solver tolerances,
an important property for the stability of the advection-diffusion
equation\cite{cesmelioglu2022compatible, johnson2009numerical}.
In addition to its favorable mass-conserving property, the 
Brezzi-Douglas-Marini and discontinuous Galerkin (BDM-DG) discretization scheme 
we employed for the Stokes equations
lets us impose the impermeability condition strongly, and the tangential
traction boundary condition weakly, without any tailored approach,
since these boundary conditions appear naturally in the weak form of the
Stokes equations~(\Cref{subsec:appendixA1}). If instead e.g. Taylor-Hood
elements were to be used, the impermeability boundary condition must
be handled with for example a Nitsche method~\cite{Nitsche1971UberSind}
or with a Lagrange multiplier~\cite{Babuska1973TheMultipliers,
Bertoluzza2017BoundaryHemodynamics}.
